\section{Conclusions \& Future Work}
\label{conclusion}

The WORG method provides a deployment schedule optimizer that converges
both closely enough and fast enough to be used inside
of a nuclear fuel cycle simulator. The algorithm can consistently obtain
tolerances of half-a-percent to a percent (1 GWe distances for over 200 GWe
deployable) for the once-through fuel cycle featured here within only five to
ten simulations. Such optimization problems are made
more challenging due to the integral nature of facility deployment and
that any demand curve may be requested.

WORG works by setting up a Gaussian process to model the production
as a function of time and the deployment schedule. This model may then
be evaluated orders of magnitude faster than running a full simulation, enabling
the search over many potential deployment schedules. The quality of these
possible schedules is evaluated based on the dynamic time warping distance
to the demand curve. The lowest distance curve is then evaluated in a
full fuel cycle simulation. The production curve that is computed by the
simulator in turn goes on to update the Gaussian process model and the
cycle repeats until the limiting conditions are met.

However, choosing the deployment schedules to estimate with the Gaussian
process may be performed in a number of ways. A blind approach would
simply be to choose such schedules randomly from a univariate. However,
the WORG method has more information available to it that helps drive
down the number of loop iterations. The first method discussed remains
stochastic but uses the inverse DTW distances of the GP model to
weight the deployment options, falling back to a Poisson distribution as
necessary. This second method minimizes the model distance for each point
in time from start to end, iteratively building up a solution. Finally,
another estimation strategy tries both previous options and chooses the
best result, forcing the stochastic method two of every four iterations
to avoid deterministic loops.  It is this last all-of-the-above method
that is seen to converge the fastest and to the lowest distance in most
cases.

It is important to note that the WORG algorithm is applicable to any
demand curves and fuel cycle facility types. It is not restricted to
reactors and power. Enrichment and separative work units, reprocessing
and separations capacity, and deep geologic repositories and their
space could be deployed via the WORG method for any applicable demand
curve. Furthermore, several of these demands and deployments can be
examined simultaneously. For instance, deployment schedules for light-water,
fast reactors, pebble-bed reactors, and separations facilities may be optimized
together on the joint
bases of minimizing cost, minimizing separated transuranics, and achieving
a specified power demand. The WORG algorithm fully supports such multivariate
problems. Reactors and power generation were chosen for study here as the
representative keystone example, though the algorithm is not tied to this
particular problem.

The speed of convergence of the WORG algorithm is effectively required for
high-fidelity simulation optimization. Single realizations may take hours or
longer to run. Executing hundred, thousands, or more realizations becomes
impractical. On the other hand, lower fidelity simulations that have short
execution times may be perfectly well optimized by an \emph{ex situ}
method. With fast run times, WORG would be implemented \emph{in situ} as
a mechanism for automation and avoiding external wrapper codes implicit
in an \emph{ex situ} optimizer. The speed of convergence for lower fidelity
simulations, while desirable conceptually, is not required in practice.

The next major step for this work is to actually employ the WORG method in
a fuel cycle simulator.  However, to the best knowledge of the
author, no existing simulator is capable of spawning forks of itself
during run time, rejoining the processes, and evaluating the results of the
child simulations in the parent simulation. Concisely, while many simulators
are `dynamic' in the fuel cycle sense, none are `dynamic' in the programming
language sense. This latter usage of the term is what is required to
take advantage of any sophisticated \emph{in situ} deployment optimizer.
The Cyclus fuel cycle simulator looks most promising as a platform
for such work to be undertaken. However, many technical roadblocks
on the software side remain, even for Cyclus.

Additionally, the WORG method does not utilize an expected decommissioning
schedule. If it is known prior to the simulation, this information
could help focus on a deployment schedule solution faster and more precisely.
Future work on WORG will consider optionally providing the decommissioning information.
This will likely affect the initial two optimizer cases and the
$M_p$ and $N_p$ deployment bounds.

Furthermore, adding \emph{in situ} capability also adds the additional
degree of freedom of how often to run the deployment schedule optimizer.
Running WORG each and every
time step seems excessive \emph{a priori}. Is every year, five years,
or ten years sufficient? How does this degree of freedom balance with the
time horizon $T$ specified in the optimizer? These questions remain unanswered, even
in a heuristic sense, and thus the frequency of optimization will be a key
parameter in a future \emph{in situ} study.
