\section{The WORG Method}
\label{method}

In order to describe the WORG method, first it is is useful to define
notation for demand curves and their parameterization.  Call $t$ the time
[years] up to some maximal time horizon $T$ (e.g. 50 years) over which time
the demand curve is known.  Then call $f(t)$ the demand curve in the natural
units of the facility type (such as [GWe] for reactors).
$f(t)$ may be any function that is desired, including non-differential
functions. Moreover, $f(t)$ need not return a simple scalar.  In a
multiobjective case, this function would return a vector of independent
objective values.
For example, though, the demand curve for a 1\% growth rate
starting at 90 [GWe] has the following form:
\begin{equation}
\label{f-1}
f(t) = 90\times 1.01^t
\end{equation}
Additionally, call $\Theta$ the deployment schedule for the facilities that
may be constructed to meet the demand.
$\Theta$ is a sequence of $P$ parameters, indexed by $p$, as seen in
Equation \ref{Theta}.
\begin{equation}
\label{Theta}
\Theta = \left\{\theta_1, \theta_2, \ldots, \theta_P\right\}
\end{equation}
Each $\theta_p$ represents that number of facilities to deploy on its
time step. In simple cases where there is only one type of facility
to deploy $P == T$.  However, when the deployment schedules of multiple
facility types are needed to meet the same demand curve, $P > T$.  The usual
example for $P > T$ is for transition scenarios which necessarily require
multiple kinds of reactors.

Now denote $M$ as the sequence for the minimum number of facilities deployable
for each deployment parameter. Also, call $N$ the sequence of the maximum number
of facilities deployable. The deployment parameters are thus each defined
on the range $\theta_p \in [M_p, N_p]$. Furthermore, because only whole
numbers of facilities may be deployed $\theta_p \in \N$.  It is also typical,
but not required, for $M = \mathbf{0}$. Zero is also the lower bound
for all possible $\theta_p$ as facilities may not be forcibly retired via the
deployment schedule.

From here, call $g(t, \Theta)$ the production as a function of time for a
given deployment schedule. This has the same units as the demand curve.
Thus for power demand and reactor deployments, $g$ is in units of [GWe]. The
optimization problem can now be posed as an attempt to find a $\Theta$
that minimizes the difference between $f$ and $g$.

\input{dtw}
\input{gp}
\input{algo}
